---
title: "run_analysis"
author: "shradheya"
date: "3/31/2020"
output: html_document
---

# Starting with loading "dplyr.

```{r}
#Load library

library(dplyr)
```

# Loading data.

```{r}
#Reading train set using read.table function because it is a tabular data.

train_x <- read.table("getdata_projectfiles_UCI HAR Dataset/UCI HAR Dataset/train/X_train.txt")
train_y <- read.table("getdata_projectfiles_UCI HAR Dataset/UCI HAR Dataset/train/y_train.txt")
train_sub <- read.table("getdata_projectfiles_UCI HAR Dataset/UCI HAR Dataset/train/subject_train.txt") 

#Reading test set using read.table function because it is a tabular data.

test_x <- read.table("getdata_projectfiles_UCI HAR Dataset/UCI HAR Dataset/test/X_test.txt")
test_y <- read.table("getdata_projectfiles_UCI HAR Dataset/UCI HAR Dataset/test/y_test.txt")
test_sub <- read.table("getdata_projectfiles_UCI HAR Dataset/UCI HAR Dataset/test/subject_test.txt")

# Reading activity lables

active_lable <- read.table("getdata_projectfiles_UCI HAR Dataset/UCI HAR Dataset/activity_labels.txt")

# Reading features

features <- read.table("getdata_projectfiles_UCI HAR Dataset/UCI HAR Dataset/features.txt")

```

# Merging train, test and, subject data [train_x with test_x], [train_y with test_y] and [train_sub with test_sub].

```{r}
# Merging x
merge_x <- rbind(train_x, test_x)

# Merging y
merge_y <- rbind(train_y, test_y)

# Merging subjects
merge_sub <- rbind(train_sub, test_sub)
```

# Selecting all  the "mean" and "std" from "features" 

```{r}
features_selected <- features[grep("mean|std",features[,2]),]
merge_x <- merge_x[,features_selected[,1]]
```

# Nameing activities in the merged data by descriptive activity name.

```{r}
colnames(merge_y) <- "label"
merge_y$activity <- factor(merge_y$label, labels = as.character(active_lable[,2]))
activity <- merge_y$activity
```

# Labeling the data with descriptive variable names.

```{r}
colnames(merge_x) <- features[features_selected[,1],2]
```


# From the data set in above step, creates a second, independent tidy data set with the average of each variable for each activity and each subject.

```{r}
colnames(merge_sub) <- "subject"
combine <- cbind(merge_x, activity, merge_sub)
temp <- group_by(combine,activity, subject)
final <- summarize_all(temp,funs(mean))
```

# Writing tidy data "tidy_data.txt"

```{r}
write.table(final, file = "./tidy_data.txt", row.names = FALSE, col.names = TRUE)
```
